Fusion Moves for Correlation Clustering

### 2014-11-12 paper/introduction-new.tex

Another line of work uses move making algorithm 
to optimize correlation clustering~\cite{bansal_2004_ml,beier_2014_cvpr,Kernighan-1970}.
Starting with an initial segmentation, auxiliary max-cut problems are approximately solved,
such that the segmentation is strictly improved.
As shown by Beier \etal~\cite{beier_2014_cvpr} only CGC~\cite{beier_2014_cvpr} 
can deal with large scale problems, but can also suffer on very large auxiliary problems.

@@

\vspace{0.1cm}
\noindent \textbf{Outline:} 
In Sec.~\ref{sec:problem_formulation} we will give a 
detailed problem definition where we introduce 
the correlation clustering objective.
In Sec.~\ref{sec:cc_fm} we describe our proposed
method and show the properties of the algorithm.
In Sec.~\ref{sec:exp} we show an evaluation
of the proposed methods methods and state of the art
and conclude in Sec.~\ref{sec:future} and\ref{sec:conclusion}.
%-------------------------------------------------------------------------

\section{Notation and Problem Formulation}\label{sec:problem_formulation}
Let $G=(V,E, w)$ be a weighted graph of nodes $V$ and edges $E$.
%
The function $w : E \rightarrow \mathbb{R}$ assigns a weight to each edge.
We will use $w_e$ as a shorthand for $w(e)$.
A positive weight expresses the desire that two adjacent nodes should
be merged, whereas a negative weight indicates
that these nodes should be separated into two different regions.
%
%A \emph{subgraph} $G_A = \{A, E_A, w\}$ consists
%of nodes $A \subseteq V$ and edges $E_A := E\cap (A\times A)$.
%
A segmentation of the graph $G$ can by either given by an 
node labeling $l \in \mathbb{N}^{|V|}$
or an edge labeling $y \in\{0,1\}^{|E|}$, \cf Fig.~\ref{fig:notation} .
An edge labeling is only consistent if it contains no dangling edges~\cite{kappes_2013_arxiv}.
We denote the set of all consistent edge labelings by $P(G)\subset\{0,1\}^{|E|}$.
The convex hull of this set is known as the \emph{multicut polytope} $MC(G) = \textrm{conv}(P(G))$.

>>>>

Another line of work uses move making algorithms 
to optimize correlation clustering~\cite{bansal_2004_ml,beier_2014_cvpr,Kernighan-1970}.
Starting with an initial segmentation, auxiliary max-cut problems are approximately solved,
such that the segmentation is strictly improved.
As shown by Beier \etal~\cite{beier_2014_cvpr} only CGC~\cite{beier_2014_cvpr} 
can deal with large scale problems, but can also suffer on very large auxiliary problems.

@@

\vspace{0.1cm}
\noindent \textbf{Outline:} 
In Sec.~\ref{sec:problem_formulation} we will give a 
detailed problem definition where we introduce 
the correlation clustering objective.
In Sec.~\ref{sec:cc_fm} we describe our proposed
method and show the properties of the algorithm.
In Sec.~\ref{sec:exp} we show an evaluation
of the proposed methods methods and state of the art
and conclude in Sec.~\ref{sec:future} and \ref{sec:conclusion}.
%-------------------------------------------------------------------------

\section{Notation and Problem Formulation}\label{sec:problem_formulation}
Let $G=(V,E, w)$ be a weighted graph of nodes $V$ and edges $E$.
%
The function $w : E \rightarrow \mathbb{R}$ assigns a weight to each edge.
We will use $w_e$ as a shorthand for $w(e)$.
A positive weight expresses the desire that two adjacent nodes should
be merged, whereas a negative weight indicates
that these nodes should be separated into two different regions.
%
%A \emph{subgraph} $G_A = \{A, E_A, w\}$ consists
%of nodes $A \subseteq V$ and edges $E_A := E\cap (A\times A)$.
%
A segmentation of the graph $G$ can by either given by an 
node labeling $l \in \mathbb{N}^{|V|}$
or an edge labeling $y \in\{0,1\}^{|E|}$, \cf Fig.~\ref{fig:notation}.
An edge labeling is only consistent if it contains no dangling edges~\cite{kappes_2013_arxiv}.
We denote the set of all consistent edge labelings by $P(G)\subset\{0,1\}^{|E|}$.
The convex hull of this set is known as the \emph{multicut polytope} $MC(G) = \textrm{conv}(P(G))$.
